% title = test
% highlight = RpgStat,trait,save,action,RpgStatLegendarySection,RpgLegendaryDefiance,melee
\begin{ExampleBlock}[RpgStat,trait,save,action,RpgStatLegendarySection,RpgLegendaryDefiance,melee][listing side text]{test}
\begin{RpgStat}{Bom Tombadil}[
        %basics
        type={Medium Celestial, Chaotic Good},
        armor-class = {14},
        hp  = {\RpgDice{12d12 + 40}},
        speed       = {35 ft.},
        %stats
        str=10,  dex=  13,  con = 15,  int=9,  wis = 24, cha  = 22,
        cha-save, wis-save,
        %skills etc.
        proficiency=8,
        skills={nature (+8)},
        skills-expertise={Performance},
        damage-immunities={all damage inflicted by creatures with the \textit{Beast} type.},
       ]
    \section{Traits}        
        \trait{Pacifist} \RpgStatName{} cannot deal lethal damage. A creature reduced to 0HP by \RpgStatName{} does not die, but instead falls \textit{unconscious}, even if they are immune to this condition.
    \section{Actions}
        \save{Lullaby}[
            modifier=wis,
            dc=22,
            target=sphere,
            size=30ft,
            failure= {Fall \textit{unconscious} for \RpgDice{1d4} hours, until they take damage, or a creature uses an action to shake them awake.},
        ] Creatures with the \textit{deafened} condition or \textit{charm} immunity are unaffected.
        \melee{Begone!}[
            type=spell, modifier=cha,
            dmg=\RpgDice{3d4+\stat{cha}}, dmg-type=force,
            extra={A creature not native to the current plane must make a DC 22 Charisma saving throw or be banished to their native plane}
        ]
    \RpgStatLegendarySection{}
        \RpgLegendaryDefiance{}
        \action{Rebuke the Violent} A creature which took hostile action in the preceeding turn takes \RpgDice{2d10} psychic damage.
\end{RpgStat}
\end{ExampleBlock}
